Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-08-30 paper/ms.tex
[WIP] Update ms - discussion - JNW comments
Co-authored-by: Joshua Winn <jnwinn@princeton.edu>

\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS}

@@

% 250 word max!
\begin{abstract}
  Complex rotators (CRs) are low-mass pre-main-sequence stars with
  light curves characterized by periods of 0.2--2 days, amplitudes of
  a few percent, and slowly-evolving sharp features.  The sharp
  features might be caused by eclipsing clumps of dust or gas orbiting
  at the corotation radius.  To improve our understanding of these
  enigmatic stars, we conducted a survey for CRs using TESS
  short-cadence data collected between 2018~July and 2022~September.
  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
  new discoveries.  Our sample includes the brightest
  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
  12-502, stands out for the complexity of its light curve --- with as
  many as eight flux dips per cycle --- and the detail with which the
  evolution in each dip's amplitude and phase can be tracked over
  1{,}500 cycles.  We argue that corotating gas or dust remains the
  most viable explanation for CRs. The gas or dust is probably
  entrained by the star's magnetic field, and the sharp features may
  result from a multipolar field topology, a hypothesis supported by
  correspondences between the light curves of CRs and of two B stars
  known to have strong multipolar magnetic fields.
\end{abstract}

@@

Figure~\ref{fig:f1} illustrates two proposed models for the extrinsic
material.  The first scenario invokes opaque dust ``clumps'' that
orbit near the Keplerian corotation radius [$R_{\rm c} =
(GM/\Omega^2)^{1/3}$, where $\Omega = 2\pi/P_{\rm rot}$] and
periodically transit the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The second scenario
invokes ``prominences'', long-lived condensations of cool, dense,
marginally-ionized gas that are embedded within the hotter corona and
corotate with the star
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
These hypothetical structures are analogous to quiescent prominences
and filaments seen in the solar corona \citep[see
e.g.][]{2015ASSL..415.....V}, though rather than existing at a
fraction of the stellar radius as in the solar case, they would exist
at distances of a few stellar radii.  A final possibility is that a
thin optically-thick ring obscures a small portion of the stellar
photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
such a ring could produce sudden dips.  We do not favor this scenario
due to two issues discussed in Appendix~\ref{app:ring}.

The dust clump and prominence hypotheses are qualitatively similar,
except that one invokes opacity from dust, while the other invokes
opacity from gas, likely bound-free transitions in hydrogen or perhaps
a molecular opacity.  However unambiguous evidence in support of any
particular scenario has yet to be acquired.  Such evidence might
include a spectroscopic detection of silicate 10\,$\mu$m dust
absorption during a dip, or perhaps detection of transient Balmer-line
excesses as a function of cycle phase, similar to observations made in
systems such as AB~Dor \citep[see][]{1999ASPC..158..146C} or PTFO
8-8695 \citep{2016ApJ...830...15J}.

CRs remain mysterious because they have been both hard to discover and
hard to characterize.   They are hard to discover because they are
rare: CRs comprise $\approx$1\% of the youngest $\approx$1\% of M
dwarfs \citep{2018AJ....155..196R}.  Out of the millions of stars
monitored by K2 and TESS, about 50 CRs have been reported to date
\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
They have been hard to characterize because many of the known CRs are
relatively faint; the initial K2 discoveries
\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
distances $\gtrsim$100\,pc, yielding optical brightnesses of
$V$$\approx$15.5 to $V$$>$20.  At such magnitudes, high-resolution
time-series spectroscopy is out of reach with current facilities,
despite the potential utility of such observations.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CRs identified by our search}.
      CRs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CRs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CR candidates are light blue circles.  Unresolved
      binaries (red circles) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CRs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CR periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:catalogscatter} shows derived stellar properties for
our CR catalog, and compares the CRs against both the target star
sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CR masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass and
age range includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
radiative cores and convective envelopes
($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
We found no obvious light curve morphology differences between the two
classes.  In terms of their rotation rates relative to the Pleiades,
the CRs are among the more rapidly rotating half of M dwarfs.

The closest CR in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this work is the
first time that it has been noted as a CR.  The three brightest CRs
are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935
($T$=10.3).  The shortest period belongs to TIC~201789285, at
3.64\,hr.  The longest period belongs to TIC~405910546, at 37.9\,hr.
If the latter source turns out to be an eclipsing binary, the
next-longest would be TIC~193831684 (31.0\,hr).

The lowest mass ($\approx$$0.12$\,$M_\odot$) belongs to TIC~267953787.
The catalog contains a few other stars with similar mass.  Given the
small number of sub-stellar mass objects in our target sample, future
studies of brown dwarf photometric variability might also yield CRs,
though there could be degeneracies in interpretation with planetary
surface features such as clouds and latitudinal bands
\citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.

@@

In Section~\ref{subsec:binarity}, we found that a significant fraction
of the CRs show indications of unresolved binarity.  Excess noise
above the Gaia single-source astrometric model is common
(\ngoodhighruwe/\ngoods\ high-quality CRs with RUWE$_{\rm DR3}$$>$2),
as is the presence of multiple periods in the TESS light curves
(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
always accompanied by multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CRs).  The
latter point strongly corroborates the idea that most sources with
RUWE$_{\rm DR3}$$>$2 are intermediate separation binaries with
projected apparent separations below 1$''$, and projected physical
separations $\lesssim$50\,AU.

The multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
\citep{2019AJ....157..216W}.  Based on the same study, the peak of the
separation distribution decreases from $\approx$49\,AU for
$0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
CR sample seems either consistent or perhaps marginally higher than
the field fraction.  This could plausibly be understood in a physical
framework in which the presence of intermediate-separation binaries
causes early disk dispersal, freeing the star to contract.  The CR
phenomenon seems to require rapid rotation; thus if binary systems
tend to produce more rapidly rotating stars, we would expect a sample
of CRs to have a larger binary fraction than the field.

@@

To date, the only stars reported to show the CR phenomenon are M
dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
massive CRs in our sample, TIC~405754448 and TIC~405910546, appear to
have masses of $\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses in our sample are
$\approx$0.40\,$M_\odot$.

Based on their locations in the color--absolute magnitude
diagram and membership in LCC, both of the K dwarfs do indeed appear
to be high mass.  However in detail, both are subject to ambiguities
in interpretation.  The TIC~405910546 light curve has a unique shape,
suggestive of an eclipsing binary.  Independently, TIC~405910546 was
one of only \nrvscatterflag\ CRs flagged with a Gaia DR3 radial
velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
that TIC~405910546 might be a pre-main-sequence eclipsing binary; it
should be studied further to clarify this classification.  For
TIC~405754448, we believe that the source {\it is} an unresolved
binary, because RUWE$_{\rm DR3}$=6.8, and because the raw light curves
in Sectors 11, 37, and 38 show an additional $\approx$6.5\,day,
$\approx$0.3\% amplitude sinusoidal signal suggestive of an unresolved
photometric companion.  If TIC~405754448 is a K+M binary, then the
flux ratio between the primary and secondary would be expected to be
$\approx$10:1.  It would be challenging for the M dwarf to produce the
observed 12.9\,hr signal with such a flux deficit, but not impossible.
While both of these objects suggest that the CR phenomenon may extend
up in mass to pre-main-sequence K dwarfs, more data are needed to
fully substantiate this claim.

@@

We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
an ``ambiguous'' CR with a 10.8\,hr period, because this period
minimized the dispersion in the phase-folded light curve.  More
careful inspection however showed that it is an impostor:
this source is a photometric blend of two ordinary rotating stars with
$P_0$=3.60\,hr, and $P_1$=5.41\,hr, with a beat period $(P_0^{-1} -
P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
for CRs: two rapidly-rotating stars with near-integer ratios of
rotation periods.  The beat between the two rotation signals produces
the apparent CR signal.  Such false positives can be excluded through
careful accounting of all peaks in a periodogram.  For instance,
TIC~435903839 shows a peak at 16.27\,hr, which is not an integer
multiple of the dispersion-minimizing 10.82\,hr period.

@@

TIC~142173958 and TIC~425937691 both show evidence for two separate
CR signals in their TESS light curves.  For TIC~142173958, the
signals are at 11.76\,hr and 12.84\,hr.  For TIC~425937691, they are
at $\approx$4.82\,hr and $\approx$3.22\,hr, near the 3:2
commensurability.  Given that both sources have two photometric
signals and elevated RUWEs, they are probably unresolved binaries
consisting of two independent CRs.  Recent work has shown that the
orbits of binaries closer than $\lesssim$700 AU tend to be aligned
with their planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If
we assume that observing CR variability similarly requires near
edge-on viewing geometries, then we might expect a sufficiently close
binary with one CR to also have another, since the spin axes in
sufficiently close binaries would tend to be aligned.  In this
scenario, the two periods of TIC~425937691 being within $\lesssim$1\%
of the 3:2 period commensurability would simply be a coincidence.

\subsection{CRs are quasiperiodic}

A periodic signal repeats exactly; the CRs do not
(Figure~\ref{fig:evoln}).  While their periods appear to remain
constant to within measurement precision over thousands of cycles, the
light curve shapes evolve over 10 to 1{,}000 cycles.  They are
therefore {\it quasi}periodic.  While this observation is consistent
with the analyses by \citet{2022AJ....163..144G} and
\citet{2023ApJ...945..114P}, it marks a qualitative departure from the
``persistent'' {\it vs.} ``transient'' flux dip distinction described
by \citet{2017AJ....153..152S}, since all CR dips seem to be
transient over timescales of more than 1{,}000 cycles
(Figure~\ref{fig:evoln}).

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
perhaps other CRs, seem to have preferred phases.  For LP 12-502, all
of the dips happen over phases corresponding to only two thirds of the
period (Figure~\ref{fig:lp}).  The remaining third seems to be ``out
of limits'' for any dipping material.  This could be evidence that the
stellar magnetic field is strongly asymmetric, and can hold extrinsic
material at corotation, but only over two thirds of the equatorial
circle.  Alternatively, the source of the material (e.g. a
planetesimal swarm) might be distributed over an arc of the same
angular extent (240$^\circ$).  We favor the former explanation, for
reasons discussed below.

@@

The asymmetry of a dip can help diagnose the optical depth of the
occulting material as a function of orbital phase angle.  Sharp
leading edges with trailing exponential egresses for instance have
been previously seen for transiting exocomets and disintegrating rocky
bodies
\citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.

Examining Figure~\ref{fig:cqvs}, it is not obvious whether CRs as a
whole show any preference for sharper ingresses, or sharper egresses.
In some cases (e.g. TIC~425933644), the continuum itself is not
well-defined, and so the meaning of ``ingress'' and ``egress'' are not
clear.  In others, such as Sector~36 of TIC~89463560, there is a
single clear sharp ingress with an exponential egress, which could be
fitted using e.g.~a model analogous to those used for exocomets
\citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z}.  The main quantities of interest
in such models would be the exponential decay time- and therefore
length-scale, as well as the impact parameter and the inferred transit
depth (and its implications for the equivalent ``radius'' of the
transiting cloud).  We briefly explored such models, until it
became clear that careful modeling of sources such as LP
12-502 merits its own in-depth study.  Connections could likely also
be made to the toroidal geometries that can be produced by outflowing
atmospheres of transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

\subsection{Dust, or gas?}

We believe that the most likely scenarios to explain CRs are either
the dust clump scenario or the prominence scenario
(Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
magnetically confined at the corotation radius.  The prominence idea
has a longer history, based on analogy with quiescent
prominences/filaments observed to exist in the solar corona for up to
a few weeks \citep[see][]{2015ASSL..415.....V}.  In an extrasolar
context, spectroscopic detections of transient Balmer- and
resonance-line absorption seen for stars such as AB~Dor and Speedy~Mic
\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
led to the interpretation that the data could best be explained by
similar structures: cold, minimally ionized hydrogen clouds or
filaments that scatter chromospheric emission from the star to produce
the observed spectroscopic line variations
\citep[see][]{1989MNRAS.238..657C}.  The short-term mechanical
stability of such gas configurations is theoretically plausible
\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and the
interpretation of this class of observations seems at least somewhat
secure.

>>>>

%\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Rotators from TESS}
\title{Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS}

@@

% 250 word max!
\begin{abstract}
%  This work focuses on a subset of low-mass pre-main-sequence stars
%  with rotation periods of 0.2--2 days, optical variability amplitudes
%  of a few percent, and sharp recurring light curve features that last for
%  hundreds of cycles.  The sharp features are probably caused by
%  eclipsing clumps of dust or gas orbiting at the corotation radius.
%  We therefore refer to the objects as ``transient corotating clumps''
%  (TCCs).
%
  Complex rotators (CRs) are low-mass pre-main-sequence stars with light
  curves characterized by periods of 0.2--2 days, amplitudes of a few
  percent, and slowly-evolving sharp features.  The sharp features
  might be caused by eclipsing clumps of dust or gas orbiting at the
  corotation radius.
  To improve our understanding of these
  enigmatic stars, we conducted a survey for CRs using TESS
  short-cadence data collected between 2018~July and 2022~September.
  Our search of \nstarssearched\ K and M dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CRs, most of which are
  new discoveries.  Our sample includes the brightest
  ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and oldest
  ($\approx$200\,Myr) known CRs.  One of the new discoveries, LP
  12-502, stands out for the complexity of its light curve --- with as
  many as eight flux dips per cycle --- and the detail with which the
  evolution in each dip's amplitude and phase can be tracked over
  1{,}500 cycles.  We argue that corotating gas or dust remains the
  most viable explanation for CRs. The gas or dust is probably
  entrained by the star's magnetic field, and the sharp features may
  result from a multipolar field topology, a hypothesis supported by
  correspondences between the light curves of CRs and of two B stars
  known to have strong multipolar magnetic fields.
\end{abstract}

@@

Figure~\ref{fig:f1} illustrates two proposed models for the extrinsic
material.  The first scenario invokes opaque dust ``clumps'' that
orbit near the Keplerian corotation radius [$R_{\rm c} =
(GM/\Omega^2)^{1/3}$, where $\Omega = 2\pi/P_{\rm rot}$] and
periodically transit the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The second scenario
invokes ``prominences'', long-lived condensations of cool, dense,
marginally-ionized gas that are embedded within the hotter corona and
that corotate with the star
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
These hypothetical prominences are analogous to quiescent prominences
and filaments seen in the solar corona \citep[see
e.g.][]{2015ASSL..415.....V}, though rather than existing at a
fraction of the stellar radius as in the solar case, they would exist
at distances of a few stellar radii.  A final possibility is that an
optically-thick ring obscures a small portion of the stellar
photosphere \citep{2019ApJ...876..127Z}.  Hot spots passing behind
such a ring could produce sudden dips.  We do not favor this scenario
(see Appendix~\ref{app:ring}).

The dust clump and gas prominence hypotheses are geometrically
indistinguishable; one could imagine dust or gas accumulating in
either of the geometries shown in Figure~\ref{fig:f1}.  The main
distinguishing factor between the two models is the composition of the
occulting material.   ``Dust clumps'' invoke opacity from dust, which
would need to be collisionally charged \citep{2023MNRAS.518.4734S}.
``Gas prominences'' invoke opacity from partially-ionized gas, likely
bound-free transitions in hydrogen or perhaps a molecular opacity.
Unambiguous evidence in support of either scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

In both models, the corotation radius is the location at which matter
concentrates.  This is empirically justified by the observation that
the sharp CR features are superposed over smooth, quasi-sinusoidal
starspot profiles.  The theoretical importance of the corotation
radius has been discussed in studies of rapid magnetic rotators,
including neutron stars \citep[e.g.]{1973ApJ...184..271L}, magnetic
massive stars \citep[e.g.][]{1985Ap&SS.116..285N}, and accreting T
Tauri stars \citep[e.g.][]{2005ApJ...634.1214L}.  In regions where the
magnetic field dominates the flow (i.e.  $B^2/8\pi > \rho v^2 /2$),
matter is dragged along with the field lines.  Assuming a dipolar
magnetic field geometry, then the tendency of both gas and dust to
become trapped at corotation is tied to how of the four relevant
forces -- gravity, Lorentz, inertial Coriolis, and inertial
centrifugal -- the Lorentz and Coriolis only act perpendicular to
field lines, while gravity and the centrifugal force are in balance at
$R_{\rm c}$ \citep[e.g.][Sec.~2]{2005MNRAS.357..251T}.  Another way to
phrase this statement is that there is a local minimum in the
effective potential of the corotating frame; given a flow from the
either the star or from a tenuous accretion disk, this local potential
minimum enables material to build up \citep{2005MNRAS.357..251T}.

While theoretical heritage for understanding rapid magnetic
rotators exists, CRs have remained mysterious because they have been both
hard to discover and hard to characterize.   They are hard to discover
because they are rare: CRs comprise $\approx$1\% of the youngest
$\approx$1\% of M dwarfs \citep{2018AJ....155..196R}.  Out of the
millions of stars monitored by K2 and TESS, about 50 CRs have been
reported to date
\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
They have been hard to characterize because many of the known CRs are
relatively faint; the initial K2 discoveries
\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
distances $\gtrsim$100\,pc, yielding optical brightnesses of
$V$$\approx$15.5 to $V$$>$20.  At such magnitudes, high-resolution
time-series spectroscopy is out of reach with current facilities,
despite the potential utility of such observations.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CRs identified by our search}.
      CRs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CRs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CR candidates are light blue circles.  Unresolved
      binaries (red circles) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CRs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CR periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Referring back to Figure~\ref{fig:catalogscatter}, which compares the
properties of CRs with those of the search sample (top panels) and the
Pleiades \citep{2016AJ....152..114R}, we see that the typical CR
masses span 0.1-0.4\,$M_\odot$, and the typical ages span 2-150\,Myr.
This mass and age range includes both fully convective stars and stars
with a combination of radiative cores and convective envelopes, with
the dividing line at around $M_\star = 0.25\,M_\odot$
\citep{2018A&A...619A.177B}.  We found no obvious differences in light
curve morphology between CRs above and below the boundary of
0.25\,$M_\odot$.  In terms of their rotation rates relative to the
Pleiades, the CRs are among the more rapidly rotating half of M
dwarfs.

The closest CR in our catalog is DG~CVn (TIC~368129164; $d$$=$18\,pc),
a member of AB Dor.  To our knowledge, this star had not previously
been recognized as a CR.  The three brightest CRs are DG~CVn
($T$=9.3), TIC~405754448 ($T$=9.6), and TIC~167664935 ($T$=10.3).  The
shortest period, 3.64\,hr, belongs to TIC~201789285.  The longest
period, 37.9\,hr, belongs to TIC~405910546.  If the latter source
turns out to be an eclipsing binary, the longest-period CR in the
catalog would be TIC~193831684 (31.0\,hr).  By definition, we required
the periods to be below 48\,hr.

The lowest mass ($\approx$$0.12$\,$M_\odot$) belongs to TIC~267953787.
The catalog contains a few other stars with similar mass.  We cannot
rule out the possibility that CRs exist with even lower masses, given
the small number of such low-mass stars in our target sample.  Perhaps
even brown dwarfs can be CRs, although it might be difficult to
distinguish the type of variability we associate with CRs from the
usual variability of brown dwarfs caused by clouds and latitudinal
bands \citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.

@@

In Section~\ref{subsec:binarity}, we found that a significant fraction
of the CRs show indications of unresolved binarity.  Excess noise
above the Gaia single-source astrometric model is common
(\ngoodhighruwe/\ngoods\ high-quality CRs with RUWE$_{\rm DR3}$$>$2),
as is the presence of multiple periods in the TESS light curves
(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
always accompanied by multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CRs).  The
latter observation corroborates the claim that most sources with
RUWE$_{\rm DR3}$$>$2 are binaries with projected apparent separations
below 1$''$, and projected physical separations $\lesssim$50\,AU.

One possible relation between binarity and CRs is that the presence of
an intermediate-separation binary could cause early disk dispersal,
freeing the star to contract.  The CR phenomenon seems to require
rapid rotation; thus if binary systems tend to produce more rapidly
rotating stars, we would expect a sample of CRs to have a larger
binary fraction than the field.  We do not see clear evidence for such
an effect.  The multiplicity rate of M dwarfs near the Sun is
26.8$\pm$1.4\% \citep{2019AJ....157..216W}.  Based on the same study,
the peak of the separation distribution decreases from $\approx$49\,AU
for $0.30$-$0.60$\,$M_\odot$ stars, to $\approx$11\,AU for
$0.15$-$0.30$\,$M_\odot$ M dwarfs.  The multiplicity fraction in our
CR sample seems approximately consistent with this field fraction.

@@

To date, the only stars reported to show the CR phenomenon are M
dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
massive CRs in our sample, TIC~405754448 and TIC~405910546, were
assigned masses of $\approx$0.82\,$M_\odot$ and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
sample are $\approx$0.40\,$M_\odot$.

These stars' locations in color--absolute magnitude diagrams and
their probable membership in Lower Centaurus Crux both support the
conclusion that they have relatively high masses.
However in detail, both are subject to ambiguities
in interpretation.  The TIC~405910546 light curve has a unique shape,
suggestive of an eclipsing binary.  Independently, TIC~405910546 was
one of only \nrvscatterflag\ CRs flagged with a Gaia DR3 radial
velocity scatter exceeding 20\,\kms.  Combined, these factors suggest
that TIC~405910546 could be a pre-main-sequence eclipsing binary; it
should be studied further to clarify this classification.

For the other object, TIC~405754448, the evidence for binarity is
stronger.  The RUWE$_{\rm DR3}$ statistic is 6.8, and the raw light
curves in Sectors 11, 37, and 38 show both the CR signal with period
12.9\,hr and amplitude $\approx$1\% and an additional sinusoidal
signal with a period $\approx$6.5\,days and amplitude $\approx$0.3\%,
likely from a second star.  If TIC~405754448 is a K+M binary, then the
flux ratio between the primary and secondary would be expected to be
$\approx$10:1.  Thus, if the K star were the source of the CR signal,
its intrinsic variability amplitude would be $\approx$1\%, while if
the M star were responsible its intrinsic variability amplitude would
be $\approx$10\%.

In short, these two objects suggest that the CR phenomenon may extend
up in mass to pre-main-sequence K dwarfs, but more data are needed to
substantiate this claim.

@@

We originally classified TIC~435903839, with RUWE$_{\rm DR3}$=17.7, as
an ``ambiguous'' CR with a 10.8\,hr period, because this period
minimized the dispersion in the phase-folded light curve.  More
careful inspection revealed an impostor:
this source is a photometric blend of two ordinary rotating stars with
$P_0$=3.60\,hr, and $P_1$=5.41\,hr, giving a beat period $(P_0^{-1} -
P_1^{-1})^{-1}$ of 10.8\,hr.  This is a novel false positive scenario
for CRs: two rapidly-rotating stars with near-integer ratios of
rotation periods.  The beat between the two rotation signals produces
the apparent CR signal.  Such false positives can be excluded through
careful accounting of all peaks in a periodogram.  For instance,
TIC~435903839 shows a peak at 16.27\,hr, which is not an integer
multiple of the dispersion-minimizing 10.82\,hr period.

@@

TIC~142173958 and TIC~425937691 both show evidence for two separate CR
signals in their TESS light curves.  For TIC~142173958, the signals
have periods of 11.76\,hr and 12.84\,hr.  For TIC~425937691, the two
periods are 4.82\,hr and 3.22\,hr, near the 3:2 commensurability.
Given that both sources have two photometric signals and elevated
RUWEs, each source is probably an unresolved binary consisting of two
CRs.

Recent work has shown that the orbits of binaries closer than
$\lesssim$700 AU tend to be aligned with their planetary systems
\citep[e.g.][]{2022AJ....163..207C}.  If we assume that observing CR
variability requires high inclinations relative to the line of sight,
and that the inclinations in binaries are correlated, then we would
expect the detection of one CR in a binary system to raise the
probability that the other star is a CR.  The limitations of the
current catalog prevent further exploration of this issue, but it
might be interesting for future study.  Even if this scenario is
correct, it would not provide an immediate explanation for the
near-commensurability of the two periods of TIC~425937691 (the ratio
is within 1\% of 3:2).

\subsection{Transience \& special phases of CR dips}

While CR periods appear to remain constant to within measurement
precision over thousands of cycles, the light curve shapes evolve over
typical timescales of 10 to 1{,}000 cycles (e.g.
Figures~\ref{fig:evoln} and~\ref{fig:lpriver0}).  The CRs are
therefore quasiperiodic, with a characteristic dip longevity of
$\approx$100 cycles.  While this observation is consistent with the
analyses by \citet{2022AJ....163..144G} and
\citet{2023ApJ...945..114P}, it marks a qualitative departure from the
``persistent'' {\it vs.} ``transient'' flux dip distinction described
by \citet{2017AJ....153..152S}, since all CR dips seem to be transient
over timescales of more than 1{,}000 cycles (Figure~\ref{fig:evoln}).

One peculiarity of CR evolution however is that the dips do not
explore all phase angles with equal weight.  LP 12-502, and other CRs,
have preferred phases lasting for at least two years.  For LP 12-502,
all of the dips happen over phases corresponding to only two thirds of
the period (Figures~\ref{fig:lp} and~\ref{fig:lpriver0}).  The
remaining third seems to be ``out of limits'' for dips over the
timespan of observations.  This could be evidence that the stellar
magnetic field is not azimuthally symmetric.  Alternatively, the
source of the material (e.g. a planetesimal swarm) might be
distributed over an arc rather than occurring randomly around the
entire orbit.

@@

The asymmetry of a dip around the time of minimum light might be
caused by the variation in optical depth of the occulting material as
a function of orbital phase angle.  Sharp leading edges with trailing
exponential egresses, for instance, have been previously seen for
transiting exocomets and disintegrating rocky bodies
\citep[e.g.][]{2012ApJ...752....1R,2012A&A...545L...5B,2015Natur.526..546V,2019A&A...625L..13Z}.

Examining Figure~\ref{fig:cqvs}, it is clear that CR dips can be
asymmetric but it is not obvious whether there is a preference for
sharper ingresses or sharper egresses.  In some cases (e.g.
TIC~425933644), the flux variations do not resemble isolated dips,
making the meaning of ``ingress'' and ``egress'' unclear.  In other
cases, such as Sector~36 of TIC~89463560, there is a sharp drop with
an exponential return to the baseline flux, resembling the signatures
of exocomet \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
or the outflowing exospheres of certain transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

\subsection{Dust vs. gas}

Both the dust clump and the gas prominence scenario invoke clumps
of material at the corotation radius;
the main property that we believe distinguishes the two ideas is 
the composition of the material.

\subsubsection{What is a prominence?}
The prominence idea is based on an analogy with quiescent
prominences/filaments in the solar corona that last as long as a few
weeks \citep[see][]{2015ASSL..415.....V}.  In the context of the Sun,
a prominence is a clump of cold, partially ionized hydrogen viewed in
emission against the dark backdrop of space.  A filament is the same
clump of plasma, but viewed in absorption against the solar disk.  In
an extrasolar context, spectroscopic detections of transient Balmer-
and resonance-line absorption seen for stars such as AB~Dor and
Speedy~Mic
\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
have been interpreted as prominences that scatter a star's
chromospheric emission \citep[see][]{1989MNRAS.238..657C}.  The
short-term mechanical stability of such gas configurations is
theoretically plausible for such stars
\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}.   To our best
knowledge, this class of spectroscopic observation also has no viable
alternative explanations.

We performed a simple visual examination of the TESS light curves for
five prominence-hosting systems studied by
\citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
V374 Peg--and detected no CR behavior.  Assuming that
spectroscopically observable prominence systems do not turn off, this would
imply that they are not always accompanied by photometric CR-like
dips: a link between the spectroscopic prominences
that may exist around rapidly rotating low-mass stars and the CR
phenomenon has yet to be made.

\subsubsection{What is the microphysical source of opacity?}
